HPC Final Project

### 2019-05-11 report/draft.tex
Pesudocode
Add the pesudocode,  modify some typo in the draft

According to the convolution argument, we have that
\begin{align}
\mathbf{u}^F (\mathbf{x}_m) & =  \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \int_{\Omega} \tilde{H}(\mathbf{x}) e^{-2 \xi |\mathbf{x} - \mathbf{x}_m|_{\ast}^2 / \eta} \mathtt{d} \mathbf{x} \\
& \approx \sum_{\mathbf{x}_{(i)} \ \text{in equi-space grid}} \tilde{H}(\mathbf{x}_{(i)}) e^{-2 \xi |\mathbf{x}_{(i)} - \mathbf{x}_m|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_2}
\end{align}
The approximation integral is spectrally accurate since the integrand is periodic.

@@

\paragraph{Pseudo-code}
\end{document}

>>>>

According to the convolution argument, we have that
\begin{align}
\mathbf{u}^F (\mathbf{x}_m) & =  \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \int_{\Omega} \tilde{H}(\mathbf{x}) e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_m|_{\ast}^2 / \eta} \mathtt{d} \mathbf{x} \\
& \approx \frac{V}{N_{\text{grid}}} \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2} \sum_{\mathbf{x}_{(i)} \ \text{in equi-space grid}} \tilde{H}(\mathbf{x}_{(i)}) e^{-2 \xi^2 |\mathbf{x}_{(i)} - \mathbf{x}_m|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_2}
\end{align}
The approximation integral is spectrally accurate since the integrand is periodic.

@@

\paragraph{Pseudo-code}

\end{document}
